Building a continuous benchmarking ecosystem in bioinformatics

### 2025-10-27 4_plos_template/plos_latex_template.tex
Update diataxis bibrecord; remove postcodes from affiliations

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf{Building a continuous benchmarking ecosystem in bioinformatics} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
%\author[1,2,*]{Izaskun Mallona}
Izaskun Mallona\textsuperscript{1,2,*}, 
%\author[2,3]{Charlotte Soneson}
Charlotte Soneson\textsuperscript{2,3}
%\author[1,2]{Ben Carrillo}
Ben Carrillo\textsuperscript{1,2}
%\author[1,2,4]{Almut Lütge}
Almut Lütge\textsuperscript{1,2,4}
%\author[1]{Daniel Incicau}
Daniel Incicau\textsuperscript{1}
%\author[1,2]{Reto Gerber}
Reto Gerber\textsuperscript{1,2}
%\author[1,2]{Anthony Sonrel}
Anthony Sonrel\textsuperscript{1,2}
%\author[1,2,*]{Mark D. Robinson}
Mark D. Robinson\textsuperscript{1,2,*}
\\
\bigskip
\textbf{1} {Department of Molecular Life Sciences, University of Zurich, 8057 Zurich, Switzerland}
\\
\textbf{2} {SIB Swiss Institute of Bioinformatics, University of Zurich, 8057 Zurich, Switzerland}
\\
\textbf{3} Friedrich Miescher Institute for Biomedical Research, 4056 Basel, Switzerland
\\
\textbf{4} Swiss Data Science Centre, 8092 Zurich, Switzerland
\bigskip

@@

\begin{table}[]
    \caption[Overview of commonly-used open-source licenses in benchmarking studies.]{Overview of commonly used open-source licenses in benchmarking studies. Code or data with restrictions to redistribute or modify are not suitable for collaborative benchmarking. \emph{License}: license name. \emph{Redistribution}: right to redistribute, e.g., reuse in another benchmark/somewhere else. \emph{Modification}: right to modify the code to produce derivative works, e.g., in another benchmark/somewhere else. \emph{Sublicensing}: for derivative works, obligation to keep the same license or freedom to be licensed differently (even copyright). Relevant if the code contributor does not want derivative works to be `closed source' or copyrighted. \emph{Commercial use}: for derivative works, whether commercial usage is restricted or not. Relevant to code contributors not willing commercial reuse of their code (by others). \emph{Attribution}: for derivative works, obligation to attribute original author(s). Relevant to code contributors willing their names/authorship to be credited in derivative works. \emph{Linking}: dynamic or static linking / use as libraries. Particularly important for metrics, as these code can be frequently incorporated (=executed) across benchmarks. }
    \vspace{0.5cm}
    \centering
%    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    License       &  Redistribution       &   Modification   & Sublicensing  & Commercial use & Attribution    & Linking   \\ \hline
    no license	& not allowed	& not allowed	& no sublicensing	& not allowed	& required	& not allowed	 \\
    GPLv3 &   	allowed	 & with restrictions	& GPLv3-compatible	& allowed	& required	& GPLv3-compatible \\
    Apache &	allowed &	allowed	& minimal restrictions	& allowed	& required	& allowed \\
    MIT	& allowed	& allowed	& full freedom	& allowed	& required	& allowed	 \\
    Public Domain	& allowed	& allowed	& full freedom	& allowed	& not required	& allowed  \\
    \textsc{CC-BY-NC-ND}	& allowed	& not allowed&	(no derivatives)	& not allowed	& required &	(not a code license)	 \\
    \textsc{CC-BY-SA-NC}	& allowed	& allowed	& not more restrictive& 	not allowed &	required	& (not a code license)	 \\
    \textsc{CC-BY-SA}	& allowed	& allowed	& not more restrictive &	allowed	& required&	(not a code license)  \\
    \textsc{CC-BY} &	allowed	& allowed	& full freedom 	& allowed& 	required&	(not a code license) \\ \hline

    \end{tabular}
%    \end{adjustbox}
    \label{tab:licenses}
\end{table}

>>>>

% too adjust the width of a very wide table
\usepackage{adjustbox}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf{Building a continuous benchmarking ecosystem in bioinformatics} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
%\author[1,2,*]{Izaskun Mallona}
Izaskun Mallona\textsuperscript{1,2,*}, 
%\author[2,3]{Charlotte Soneson}
Charlotte Soneson\textsuperscript{2,3}
%\author[1,2]{Ben Carrillo}
Ben Carrillo\textsuperscript{1,2}
%\author[1,2,4]{Almut Lütge}
Almut Lütge\textsuperscript{1,2,4}
%\author[1]{Daniel Incicau}
Daniel Incicau\textsuperscript{1}
%\author[1,2]{Reto Gerber}
Reto Gerber\textsuperscript{1,2}
%\author[1,2]{Anthony Sonrel}
Anthony Sonrel\textsuperscript{1,2}
%\author[1,2,*]{Mark D. Robinson}
Mark D. Robinson\textsuperscript{1,2,*}
\\
\bigskip
\textbf{1} {Department of Molecular Life Sciences, University of Zurich, Zurich, Switzerland}
\\
\textbf{2} {SIB Swiss Institute of Bioinformatics, University of Zurich, Zurich, Switzerland}
\\
\textbf{3} Friedrich Miescher Institute for Biomedical Research, Basel, Switzerland
\\
\textbf{4} Swiss Data Science Centre, Zurich, Switzerland
\bigskip

@@

\begin{table}[]
    \caption[Overview of commonly-used open-source licenses in benchmarking studies.]{Overview of commonly used open-source licenses in benchmarking studies. Code or data with restrictions to redistribute or modify are not suitable for collaborative benchmarking. \emph{License}: license name. \emph{Redistribution}: right to redistribute, e.g., reuse in another benchmark/somewhere else. \emph{Modification}: right to modify the code to produce derivative works, e.g., in another benchmark/somewhere else. \emph{Sublicensing}: for derivative works, obligation to keep the same license or freedom to be licensed differently (even copyright). Relevant if the code contributor does not want derivative works to be `closed source' or copyrighted. \emph{Commercial use}: for derivative works, whether commercial usage is restricted or not. Relevant to code contributors not willing commercial reuse of their code (by others). \emph{Attribution}: for derivative works, obligation to attribute original author(s). Relevant to code contributors willing their names/authorship to be credited in derivative works. \emph{Linking}: dynamic or static linking / use as libraries. Particularly important for metrics, as these code can be frequently incorporated (=executed) across benchmarks. }
    \vspace{0.5cm}
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    License       &  Redistribution       &   Modification   & Sublicensing  & Commercial use & Attribution    & Linking   \\ \hline
    no license	& not allowed	& not allowed	& no sublicensing	& not allowed	& required	& not allowed	 \\
    GPLv3 &   	allowed	 & with restrictions	& GPLv3-compatible	& allowed	& required	& GPLv3-compatible \\
    Apache &	allowed &	allowed	& minimal restrictions	& allowed	& required	& allowed \\
    MIT	& allowed	& allowed	& full freedom	& allowed	& required	& allowed	 \\
    Public Domain	& allowed	& allowed	& full freedom	& allowed	& not required	& allowed  \\
    \textsc{CC-BY-NC-ND}	& allowed	& not allowed&	(no derivatives)	& not allowed	& required &	(not a code license)	 \\
    \textsc{CC-BY-SA-NC}	& allowed	& allowed	& not more restrictive& 	not allowed &	required	& (not a code license)	 \\
    \textsc{CC-BY-SA}	& allowed	& allowed	& not more restrictive &	allowed	& required&	(not a code license)  \\
    \textsc{CC-BY} &	allowed	& allowed	& full freedom 	& allowed& 	required&	(not a code license) \\ \hline

    \end{tabular}
    \end{adjustbox}
    \label{tab:licenses}
\end{table}
